### 2013-05-08 doc/icml2013/theory.tex
Minor changes + experiments

\begin{lemma}[lower bound on restricted strong convexity constant]
\label{lem:lowRankLower}
%Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$.
If $$n = \Omega \left(\frac{R^{4p} (p!)^2 \log(1/\delta)}{\sigmamin(\Sigma_p)^2} \right),$$
then with probability at least $1-\delta$:
$$\kappa(\opX_p) \ge \frac{\sigmamin(\Sigma_p)}{2}.$$
\end{lemma}

@@

\begin{lemma}[upper bound on adjoint operator]
\label{lem:lowRankUpper}
% Let $\opX_p$ be the linear operator previously defined. 
If $$n = \Omega \left(\max_{p\in [3]} \frac{L^{2p} S^{2p} R^{4p} \log(1/\delta)}{\left(\lambda_n^{(p)}\right)^2} \right),$$
then with probability at least $1-\delta$:
$$\lambda_n^{(p)} \ge \frac1{n} \|\opX_p^*(\eta_p)\|_\op,$$
for each $p \in \{1,2,3\}$.
\end{lemma}

>>>>

\begin{lemma}[lower bound on restricted strong convexity constant]
\label{lem:lowRankLower}
%Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$.
If $$n = \Omega \left(\max_{p\in [3]} \frac{R^{4p} (p!)^2 \log(1/\delta)}{\sigmamin(\Sigma_p)^2} \right),$$
then with probability at least $1-\delta$:
$$\kappa(\opX_p) \ge \frac{\sigmamin(\Sigma_p)}{2},$$
for each $p \in [3]$.
\end{lemma}

@@

\begin{lemma}[upper bound on adjoint operator]
\label{lem:lowRankUpper}
% Let $\opX_p$ be the linear operator previously defined. 
If $$n = \Omega \left(\max_{p\in [3]} \frac{L^{2p} S^{2p} R^{4p} \log(1/\delta)}{\left(\lambda_n^{(p)}\right)^2} \right),$$
then with probability at least $1-\delta$:
$$\lambda_n^{(p)} \ge \frac1{n} \|\opX_p^*(\eta_p)\|_\op,$$
for each $p \in [3]$.
\end{lemma}
